### 2014-05-21 prevpub.tex
Add microtype and adjust citations

Chapter~\ref{chap:learnability}~is adapted from a conference
submission that will appear as:
A.~Sivaraman, K.~Winstein, P.~Thaker, and H.~Balakrishnan
\newblock {An Experimental
  Study of the Learnability of Congestion Control}. \newblock In {\em
  SIGCOMM}, Chicago, Ill., August 2014.

>>>>

Chapter~\ref{chap:learnability}~is adapted from:
A.~Sivaraman, K.~Winstein, P.~Thaker, and H.~Balakrishnan
\newblock {An Experimental
  Study of the Learnability of Congestion Control}. \newblock In {\em
  SIGCOMM}, Chicago, Ill., August 2014 (forthcoming).
